\vspace{-10pt}Reservoir Computing Framework for Predictive Quantization of MIMO-OFDM SVD Precoders \vspace{-10pt}

### 2020-01-04 paper/main.tex
Adding cover letter

\title{\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-10pt}}

@@

 \author{\authorblockN{Agrim Gupta, Pranav Sankhe, Kumar Appaiah, Manoj Gopalkrishnan}
 \
 \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
 \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-18pt}}
% \thanks{Parts of this work was supported by the Bharti Centre for Communication in
% IIT Bombay, and the Visvesvaraya
% PhD Scheme of Ministry of Electronics \& Information Technology,
% Government of India (implemented by the Digital India Corporation).
% }}
}
\maketitle

>>>>

\title{\vspace{-10pt}Reservoir Computing Framework for Predictive Quantization of MIMO-OFDM SVD Precoders  \vspace{-10pt}}

@@

 \author{\authorblockN{Author 1, Author 2, Author 3, Author 4}
 \
 \authorblockA{Institute 1, Institute 2\vspace{-18pt}}
% \thanks{Parts of this work was supported by the Bharti Centre for Communication in
% IIT Bombay, and the Visvesvaraya
% PhD Scheme of Ministry of Electronics \& Information Technology,
% Government of India (implemented by the Digital India Corporation).
% }}
}
\maketitle
